quollr: An R Package for Visualizing $2-D$ Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-03-30 paper-quollr.Rmd
Need to fix with new version of quollr

## Tests

All functions have tests written and implemented using the \CRANpkg{testthat} package in R. These tests illuminated issues, allowing meaningful changes and providing insights into some pitfalls of the package. For example, several tests check if there is an NLDR point at the intersection of two bins and determine which bin this point falls into.

Figure xx shows an example of a simulated test set. When creating this test data set,

<!--discuss a test with how a point in a intersection of two hexagonal going to evaluate-->
<!--selecting the default values to q as 0.1-->

@@

>>>>

### Interactivity

<!-- ## Tests -->

<!-- All functions have tests written and implemented using the \CRANpkg{testthat} package in R. These tests illuminated issues, allowing meaningful changes and providing insights into some pitfalls of the package. For example, several tests check if there is an NLDR point at the intersection of two bins and determine which bin this point falls into. -->

<!-- Figure xx shows an example of a simulated test set. When creating this test data set,  -->

<!-- <!--discuss a test with how a point in a intersection of two hexagonal going to evaluate--> -->
<!-- <!--selecting the default values to q as 0.1--> -->

# Example

@@

Need to find another application
